---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  paged.print=FALSE
)
```

# geocoder

<!-- badges: start -->
<!-- badges: end -->

The goal of `geocoder` is to provide geocoding service for R users.

## Installation

To install this package

## Geocoding

User could use `geocoding` function to obtain the spatial information from a given address. User may pass in one or multiple address all at once.

The data structure returned from the `geocoding` function is specified as follows:

- address: the address specified by the user
- lat: latitude
- lng: longitude 
- county: county name
- zip_geocode: zip code from the best-matched geocoding result
- status_geocode: TRUE if a valid result is founded, otherwise FALSE
- importance: the accuracy score from the nominatim geocoding service
- service: the service used (nominatim is prioritize and US census API comes second)

```{r  paged.print=FALSE}
library(geocoder)

address <- "Robinwood Avenue, Whitehall, Franklin County, Ohio, 43213, United States"
result <- geocoding(address)
result
```

```{r paged.print=FALSE}
address_list <- 
  c(
     "Robinwood Avenue, Whitehall, Franklin County, Ohio, 43213, United States",
     "Hamilton Road, East Hamilton Plaza, Whitehall, Franklin County, Ohio, 43125, United States",
     "Target, 3955, East Broad Street, Whitehall, Franklin County, Ohio, 43213, United States",
     "Josephus Lane, Whitehall, Franklin County, Ohio, 43227, United States",
     "Chandler Drive, Whitehall, Franklin County, Ohio, 43213, United States",
     "Enterprise, East Broad Street, East Broad Plaza Apartments, Whitehall, Franklin County, Ohio, 43004, United States"
  )

geocoding(address_list)
```

To specify the service to use, user could use `geocoding_nominatim` or `geocoding_census`. 

```{r paged.print=FALSE}
# Use US Census API
geocoding_census(address = address)

# Use Nominatim
geocoding_nominatim(address = address, threshold = 0.5)
```

Note that these two functios only works for single address input. To geocode multiple addresses with specified service, wrap the function with a for-loop or use the `map` family functions.

```{r paged.print=FALSE}
purrr::map_dfr(
  .x = address_list,
  .f = geocoding_nominatim
)
```

## Reverse Geocoding

Sometimes only lat and lng is provided but you would like to have other spatial information such as zipcode, county, city and etc. You could use `geocoding_nominatim_reverse` to reverse geocoding. 

```{r paged.print=FALSE}
geocoding_nominatim_reverse(
  lat = 39.96893,
  lng = -82.8964
)
```

## Geocoding with Spatial Shapefiles
`geocoding_sf` is designed when you have a shapefile that contains serveral spatial regions and you wold like to know which region your data falls into. 

```{r eval = FALSE}
geocoding_sf(
  lat = lat,
  lng = lng,
  sf = sf,     # spatial object
  id = "name", # the identifier column of the sf object
  parallel = FALSE # parallel execution
)
```







